Web-based Supplementary Materials for A Space-time \Skewt Model for Threshold Exceedances by Morris, Reich, Thibaud, and Cooley

### 2016-12-09 LaTeX/supplemental_rev_2.tex
edits for final submission

% cross-referencing appendices
\usepackage{xr}
\externaldocument{skewt_rev}

@@

\section{Proof that $\lim_{h \rightarrow \infty} \pi(h) = 0$} \label{sta:proofsamepartition}
Let $c$ be the midpoint of $\bs_1$ and $\bs_2$.
Define $A$ as the circle centered at $c$ with radius $h / 2$ where $h = ||\bs_1 - \bs_2||$ is the distance between sites $\bs_1$ and $\bs_2$.
Consider a homogeneous spatial Poisson process over $A$ with intensity $\lambda_{PP}$, so that
\begin{align*}
  \mu_{PP}(A) = \lambda_{PP} |A| = \lambda_{PP} \pi \left(\frac{h}{2}\right)^2 = \lambda_{PPA}^* h^2.
\end{align*}
Consider a partition of $A$ into four regions, $B_1$, $B_2$, $R_1$, $R_2$ as seen in \fref{stfig:hpp}.
\begin{figure}
  \includegraphics[width=\linewidth]{plots/circles}
  \caption{Illustration of the partition of $A$.}
  \label{stfig:hpp}
\end{figure}
Let $N_i$ be the number of knots in $B_i$ and $L_i = l$ if $\bs_i \in P_l$ for $i = 1, 2$.
Then
\begin{align}
  P(L_1 \neq L_2) \ge P(N_1 > 0, N_2 > 0)
\end{align}
since knots in both $B_1$ and $B_2$ is sufficient, but not necessary, to ensure that $\bs_1$ and $\bs_2$ are in different partition sets.
By definition of a Poission process, $N_1$ and $N_2$ are independent and thus $P(N_1 > 0, N_2 > 0) = P(N_1 > 0)^2$, and
\begin{align}
  \mu_{PP}(B_1) &= \lambda_{PP} |B_1| = \lambda_{PP} \frac{h^2}{4} \left(\frac{2 \pi}{3} - \frac{\sqrt{3}}{2} \right) \nonumber \\
       &= \lambda^*_{PPB1} h^2.
\end{align}
So,
\begin{align}
  P(L_1 \neq L_2) >= P(N_1 > 0)^2 = [1 - P(N_1 = 0)]^2 = [1 - \exp\left(-\lambda^*_{PPB1} h^2\right)]^2
\end{align}
which goes to 1 as $h$ goes to infinity.

@@

>>>>

% cross-referencing appendices
\usepackage{xr}
\externaldocument{skewt_rev_2}

@@

\section{Proof that $\lim_{h \rightarrow \infty} \pi(h) = 0$} \label{sta:proofsamepartition}
Let $c$ be the midpoint of $\bs_1$ and $\bs_2$.
Define $A$ as the circle centered at $c$ with radius $h / 2$ where $h = ||\bs_1 - \bs_2||$ is the distance between sites $\bs_1$ and $\bs_2$.
Consider a homogeneous spatial Poisson process over $A$ with intensity $\lambda_{PP}$, so that
\begin{align*}
  \mu_{PP}(A) = \lambda_{PP} |A| = \lambda_{PP} \pi \left(\frac{h}{2}\right)^2 = \lambda_{PPA}^* h^2.
\end{align*}
Consider a partition of $A$ into four regions, $B_1$, $B_2$, $R_1$, $R_2$ as seen in \fref{stfig:hpp}.
\begin{figure}
  \includegraphics[width=\linewidth]{plots/circles}
  \caption{Illustration of the partition of $A$.}
  \label{stfig:hpp}
\end{figure}
Let $N_i$ be the number of knots in $B_i$ and $L_i = l$ if $\bs_i \in P_l$ for $i = 1, 2$.
Then
\begin{align}
  P(L_1 \neq L_2) \ge P(N_1 > 0, N_2 > 0)
\end{align}
since knots in both $B_1$ and $B_2$ is sufficient, but not necessary, to ensure that $\bs_1$ and $\bs_2$ are in different partition sets.
By definition of a Poisson process, $N_1$ and $N_2$ are independent and thus $P(N_1 > 0, N_2 > 0) = P(N_1 > 0)^2$, and
\begin{align}
  \mu_{PP}(B_1) &= \lambda_{PP} |B_1| = \lambda_{PP} \frac{h^2}{4} \left(\frac{2 \pi}{3} - \frac{\sqrt{3}}{2} \right) \nonumber \\
       &= \lambda^*_{PPB1} h^2.
\end{align}
So,
\begin{align}
  P(L_1 \neq L_2) \ge P(N_1 > 0)^2 = [1 - P(N_1 = 0)]^2 = [1 - \exp\left(-\lambda^*_{PPB1} h^2\right)]^2
\end{align}
which goes to 1 as $h$ goes to infinity.

@@

\section{Spatial dependence of ozone} \label{sta:ozonespatdep}
In this appendix, we include a plot suggesting spatial dependence in ozone measurements.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{plots/daily-quantiles-ozone.pdf}
	\caption{Daily quantiles for two monitoring locations near Columbus, OH (left) and daily quantiles for a monitoring location in Los Angeles, CA and Columbus, OH (right)}
	\label{stfig:bivariateozone}
\end{figure}

\section{Best performing models} \label{sta:ozonemodelperf}
This appendix includes a table with the top two performing models for predicting ozone exceedance of level $L$.
\begin{table}
	\small
	\caption{Top two performing models for predicting ozone exceedance of level $L$ with Relative Brier score}
	\label{sttbl:ozoneresults}
	\centering
	\begin{tabular}{|l|l l l c|l l l c|}
		\cline{2-9}
		\multicolumn{1}{c|}{}  & \multicolumn{4}{c|}{1st} & \multicolumn{4}{c|}{2nd} \\
		\hline
		$L = q(0.90)$  & No time series & $K=6$  & $T=50$  & BS: 0.992 &
		No time series & $K=1$  & $T=0$  & BS: 0.992 \\
		$L = q(0.95)$  & Time series & $K=5$ & $T=50$ & BS: 0.988 &
		No time series & $K=6$  & $T=50$ & BS: 0.989\\
		$L = q(0.98)$  & Time series & $K=7$  & $T=50$ & BS: 0.973 &
		Time series & $K=5$ & $T=50$ & BS: 0.975\\
		$L = q(0.99)$  & No time series    & $K=8$ & $T=0$ & BS: 0.946 &
		Time series    & $K=9$  & $T=75$ & BS: 0.947\\
		$L = q(0.995)$ & No time series    & $K=8$  & $T=0$ & BS: 0.951 &
		Time series    & $K=9$ & $T=75$ & BS: 0.956\\
		\hline
	\end{tabular}
\end{table}
